Effects of the body force on the evacuation dynamics

### 2019-12-17 paper.tex
Update paper.tex
agregue los captions a las primeras figuras

We now widen the investigation on the parameter settings to include the one 
associated to the body force. We will focus on the complex interplay between 
the body force and the sliding friction among pedestrians. Recall that the 
interplay dynamics is not directly controlled by the numerical setting, but 
through dimensionless ``numbers'', where the model parameters appear mixed 
between each other. Thus, this step up offers a challenge to the 
``individualistic'' meaning of the parameter's setting.

@@

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./vd_vs_te_N225.eps}
\caption{\label{} }
\end{figure}

>>>>

We now widen the investigation on the parameter settings to include the one 
associated to the body force. We will focus on the complex interplay between 
the body force and the sliding friction among pedestrians. Recall that the 
interplay dynamics is not directly controlled by the numerical setting, but 
through dimensionless ``numbers'', where the model parameters appear mixed 
between each other. Thus, this step up offers a challenge to the 
``individualistic'' meaning of the parameter's setting. \\

@@

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./vd_vs_te_N225.eps}
\caption{\label{vd_vs_te}Mean evacuation time (s) vs. the pedestrian’s desired velocity (m/s) for a bottleneck. The room was 20 m x 20 m size. The door was 0.92 m width. Mean values were computed from 10 evacuation processes. 225 pedestrians were initially placed in a square lattice with a random initial velocity. Each process was finished when 158 pedestrians left the room. The different symbols indicate the $k$ value corresponding to the body force (see the label). }
\end{figure}

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./degree_vs_vd_multi_kn.eps}\label{degree_te}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_vd_multi_kn.eps}\label{overlap_te}}\\
\caption[width=0.47\columnwidth]{(a) Mean degree as a function of the pedestrian’s desired velocity (m/s). (b) Mean overlap as a function of the pedestrian’s desired velocity (m/s). Each symbol indicates the $k$ value corresponding to the body force (see the labels). The data corresponds to a bottleneck with periodic boundary conditions (reinjecting pedestrians). The average was taken every two seconds once the crowd reaches the stationary state ($t=$20~s) until the end of the simulation ($t=$110~s).}
\label{degree_overlap_te}
\end{figure}
